---
title: "Communities of Color"
---

```{r child = "setup.Rmd"}
```



## All Communities of Color

**Currently Serving**<br> 
94 0-2 yr<br>
831 3-5 yr

**Eligible but not Served**<br>
5871 0-2 yr<br>
4221 3-5 yr

**Percent Served**<br>
1.6% 0-2 yr<br>
19.6% 3-5 yr

```{r, layout="l-page"}
race_ethnicity_composite %>% 
  make_map()
```

<br>

```{r, layout="l-screen-inset"}
race_ethnicity_composite %>% 
  make_table()
```




## Black

**Currently Serving**<br> 
8 0-2 yr<br>
67 3-5 yr

**Eligible but not Served**<br>
165 0-2 yr<br>
214 3-5 yr

**Percent Served**<br>
4.8% 0-2 yr<br>
31.3% 3-5 yr

```{r, layout="l-page"}
race_ethnicity_black %>% 
  make_map()

```

<br>

```{r, layout="l-screen-inset"}
race_ethnicity_black %>% 
  make_table()
```


## American Indian and Alaska Native

**Currently Serving**<br> 
0 0-2 yr<br>
16 3-5 yr

**Eligible but not Served**<br>
57 0-2 yr<br>
80 3-5 yr

**Percent Served**<br>
0% 0-2 yr<br>
20% 3-5 yr

```{r, layout="l-page"}
race_ethnicity_aian %>% 
  make_map()
```

<br>

```{r, layout="l-screen-inset"}
race_ethnicity_aian %>% 
  make_table()
```


## Asian

**Currently Serving**<br> 
5 0-2 yr<br>
33 3-5 yr

**Eligible but not Served**<br>
179 0-2 yr<br>
245 3-5 yr

**Percent Served**<br>
2.8% 0-2 yr<br>
13.5% 3-5 yr

```{r, layout="l-page"}
race_ethnicity_asian %>% 
  make_map()
```

<br>

```{r, layout="l-screen-inset"}
race_ethnicity_asian %>% 
  make_table()
```


## Caucasian

**Currently Serving**<br> 
20 0-2 yr<br>
223 3-5 yr

**Eligible but not Served**<br>
1306 0-2 yr<br>
1905 3-5 yr

**Percent Served**<br>
1.5% 0-2 yr<br>
11.7% 3-5 yr

```{r, layout="l-page"}
race_ethnicity_white %>% 
  make_map()

```

<br>

```{r, layout="l-screen-inset"}
race_ethnicity_white %>% 
  make_table()
```


## Hispanic

**Currently Serving**<br> 
101 0-2 yr<br>
673 3-5 yr

**Eligible but not Served**<br>
933 0-2 yr<br>
1905 3-5 yr

**Percent Served**<br>
10.8% 0-2 yr<br>
35.3% 3-5 yr

```{r, layout="l-page"}
race_ethnicity_latino %>% 
  make_map()
```

```{r, layout="l-screen-inset"}
race_ethnicity_latino %>% 
  make_table()
```


### Where the Data Comes From

Data about children of color at each school was provided by Health Share of Oregon. 

The composite score was created by combining and generating an average of the Score Relative to Median for each individual community of color. 