---
title: "Poverty"
---

```{r child = "setup.Rmd"}
```

## Below 100% Federal Poverty Level

**Currently Serving**<br> 
134 0-2 yr<br>
314 3-5 yr

**Eligible but not Served**<br>
638 0-2 yr<br>
5742 3-5 yr

**Percent Served**<br>
21% 0-2 yr<br>
5.5% 3-5 yr

```{r, layout="l-page"}
children_in_poverty_100_fpl %>%
  make_map()
```

<br>

```{r, layout="l-screen-inset"}
children_in_poverty_100_fpl %>%
  make_table()
```

```{r}
median_value_raw <- pull_median_value(children_in_poverty_100_fpl) %>% 
  number(0.1)
```

*The median value for this table is `r median_value_raw`.*

## Between 100% and 200% Federal Poverty Level

**Currently Serving**<br> 
57 0-2 yr<br>
213 3-5 yr

**Eligible but not Served**<br>
3815 0-2 yr<br>
3659 3-5 yr

**Percent Served**<br>
1.5% 0-2 yr<br>
5.8% 3-5 yr


```{r, layout="l-page"}
children_in_poverty_between_100_200 %>%
  make_map()

```

<br>

```{r, layout="l-screen-inset"}
children_in_poverty_between_100_200 %>%
  make_table()
```


```{r}
median_value_raw <- pull_median_value(children_in_poverty_between_100_200) %>% 
  number(0.1)
```

*The median value for this table is `r median_value_raw`.*

## Below 200% Federal Poverty Level

**Currently Serving**<br> 
114 0-2 yr<br>
1054 3-5 yr

**Eligible but not Served**<br>
7177 0-2 yr<br>
6126 3-5 yr

**Percent Served**<br>
1.6% 0-2 yr<br>
17.2% 3-5 yr

```{r, layout="l-page"}
children_in_poverty_200_fpl %>%
  make_map()

```

<br>

```{r, layout="l-screen-inset"}
children_in_poverty_200_fpl %>%
  make_table()
```


```{r}
median_value_raw <- pull_median_value(children_in_poverty_200_fpl) %>% 
  number(0.1)
```

*The median value for this table is `r median_value_raw`.*


### Where the Data Comes From

Data on poverty comes from the [American Community Survey table B17024](https://censusreporter.org/tables/B17024/). 

Because this data comes at the census tract level, it was merged to match school catchment areas using methodology described on the [notes page](notes.html).

